\documentclass[11pt]{letter}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}

\begin{document}

\begin{letter}{
Prof. Binshan Lin \\
Editor-in-Chief \\
Expert Systems with Applications \\
Elsevier
}

\opening{Dear Prof. Lin,}

We are pleased to submit our manuscript entitled ``Multi-Strategy GraphRAG for Financial Institutions: Security, Grounding, and Token Economy'' for consideration for publication in \textit{Expert Systems with Applications}.

\textbf{Contribution.} This paper proposes a multi-strategy GraphRAG (Graph Retrieval-Augmented Generation) architecture specifically designed for financial institutions, jointly addressing four pillars critical to regulated environments: security, hallucination reduction, token economy, and processing speed. The system integrates a financial domain ontology, intent-aware retrieval fusion across three parallel strategies (graph traversal, vector similarity, and community summarization), a formal threat model with six defense mechanisms mapped to four regulatory frameworks (LGPD, GDPR, Basel~III, SOX), and comprehensive empirical evaluation through five experiments and three financial applications.

\textbf{Novelty.} To the best of our knowledge, this is the first work to jointly address a financial domain ontology, a formal security model for regulated multi-tenant environments, multi-strategy retrieval with intent-aware fusion, and token economy optimization---validated with a functional open-source implementation and empirical financial applications. Existing works address subsets of these challenges but none integrates all four pillars.

\textbf{Key results.} The proposed system achieves 87.4\% faithfulness (14.5 percentage points above VectorRAG), 96.4\% source attribution, 70\% token reduction compared to full-document retrieval, and 0\% cross-tenant data leakage in red-team evaluation across 200 adversarial queries.

\textbf{Journal fit.} We believe \textit{Expert Systems with Applications} is the ideal venue for this work because it bridges expert systems and applied artificial intelligence in domain-specific contexts. Our paper demonstrates a complete expert system for financial compliance, audit, and analysis, with practical implications for banks, regulators, and auditors---directly aligned with the journal's scope and readership.

\textbf{Confirmations.} We confirm that this manuscript has not been published previously, is not under consideration for publication elsewhere, and its publication is approved by all authors. The authors declare no competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

We look forward to your consideration.

\closing{Sincerely,\\[2em]
The Authors}

\end{letter}
\end{document}
